Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
updated
correzioni su una nota in sezione 5

We introduce two stopping conditions: the maximum number of sub-iterations and the condition on learning rate of Adam sub-iterations.
\todomat{I find "two stopping conditions" confusing: it's just one with an additional constraint}
We stop with inner iterations if:

>>>>

In order to cope with this behaviour we introduce an adaptive stopping condition: we permorm a new snapshot anytime the learning rate proposed by the adam optimizer in a sub-iteration is 10 times smaller than that one proposed at the immediately previous snapshot. This stopping condition is subject to a constraint on the maximum number of sub-iterations performable, which is problem dependent.
\todomat{I find "two stopping conditions" confusing: it's just one with an additional constraint}
\todobep{I tried to solve the issue here:hope it's better now}
We stop with inner iterations if:
